---
output: github_document
bibliography: bibliography.bib
csl: chicago-author-date.csl
nocite: '@*'
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.align = "center",
  fig.path = "man/figures/README-"
)
```

# **FLaMingos**: **F**unctional **L**atent dat**A** **M**odels for cluster**ING** heterogene**O**us curve**S**

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/fchamroukhi/FLaMingos.svg?branch=master)](https://travis-ci.org/fchamroukhi/FLaMingos)
[![CRAN versions](https://www.r-pkg.org/badges/version/flamingos)](https://cran.r-project.org/web/packages/flamingos/index.html)
[![CRAN logs](https://cranlogs.r-pkg.org/badges/flamingos)](https://cran.rstudio.com/web/packages/flamingos/index.html)
<!-- badges: end -->

flamingos is an open-source toolbox (available in R and in Matlab) for the 
simultaneous clustering and segmentation of heterogeneous functional data (i.e
time-series ore more generally longitudinal data), with original and flexible
functional latent variable models, fitted by unsupervised algorithms, 
including EM algorithms.

Our nice FLaMingos are mainly:

* mixRHLP;
* mixHMM;
* mixHMMR.

The models and algorithms are developped and written in Matlab by Faicel 
Chamroukhi, and translated and designed into R packages by Florian Lecocq, 
Marius Bartcus and Faicel Chamroukhi.

# Installation

You can install the **flamingos** package from [GitHub](https://github.com/fchamroukhi/FLaMingos) with:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("fchamroukhi/FLaMingos")
```

To build *vignettes* for examples of usage, type the command below instead:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("fchamroukhi/FLaMingos", 
                         build_opts = c("--no-resave-data", "--no-manual"), 
                         build_vignettes = TRUE)
```

Use the following command to display vignettes:

```{r, eval = FALSE}
browseVignettes("flamingos")
```

# Usage

```{r, message = FALSE}
library(flamingos)
```

<details>
  <summary>mixRHLP</summary>

```{r, echo=TRUE}
data("toydataset")
x <- toydataset$x
Y <- t(toydataset[,2:ncol(toydataset)])

K <- 3 # Number of clusters
R <- 3 # Number of regimes (polynomial regression components)
p <- 1 # Degree of the polynomials
q <- 1 # Order of the logistic regression (by default 1 for contiguous segmentation)
variance_type <- "heteroskedastic" # "heteroskedastic" or "homoskedastic" model

n_tries <- 1
max_iter <- 1000
threshold <- 1e-5
verbose <- TRUE
verbose_IRLS <- FALSE
init_kmeans <- TRUE

mixrhlp <- emMixRHLP(X = x, Y = Y, K, R, p, q, variance_type, init_kmeans, 
                     n_tries, max_iter, threshold, verbose, verbose_IRLS)

mixrhlp$summary()

mixrhlp$plot()
```

</details>

<details>
  <summary>mixHMM</summary>

```{r, echo=TRUE}
data("toydataset")
Y <- t(toydataset[,2:ncol(toydataset)])

K <- 3 # Number of clusters
R <- 3 # Number of regimes (HMM states)
variance_type <- "heteroskedastic" # "heteroskedastic" or "homoskedastic" model

ordered_states <- TRUE
n_tries <- 1
max_iter <- 1000
init_kmeans <- TRUE
threshold <- 1e-6
verbose <- TRUE

mixhmm <- emMixHMM(Y = Y, K, R, variance_type, ordered_states, init_kmeans, 
                   n_tries, max_iter, threshold, verbose)

mixhmm$summary()

mixhmm$plot()
```

</details>

<details>
  <summary>mixHMMR</summary>
  
```{r, echo=TRUE}
data("toydataset")
x <- toydataset$x
Y <- t(toydataset[,2:ncol(toydataset)])

K <- 3 # Number of clusters
R <- 3 # Number of regimes/states
p <- 1 # Degree of the polynomial regression
variance_type <- "heteroskedastic" # "heteroskedastic" or "homoskedastic" model

ordered_states <- TRUE
n_tries <- 1
max_iter <- 1000
init_kmeans <- TRUE
threshold <- 1e-6
verbose <- TRUE

mixhmmr <- emMixHMMR(X = x, Y = Y, K, R, p, variance_type, ordered_states, 
                     init_kmeans, n_tries, max_iter, threshold, verbose)

mixhmmr$summary()

mixhmmr$plot()
```

</details>

# References
