---
output: github_document
bibliography: bibliography.bib
csl: chicago-author-date.csl
nocite: '@*'
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.align = "center",
  fig.path = "man/figures/README-"
)
```

<!-- badges: start -->
<!-- badges: end -->

# **FLaMingoS**: **F**unctional **L**atent dat**A** **M**odels for cluster**ING** heterogene**O**us time-**S**eries

flamingos is a toolbox for the simultaneous clustering (or classification) and 
segmentation of heterogeneous functional data (i.e time-series ore more 
generally longitudinal data), with original and flexible functional latent 
variable models, fitted by unsupervised algorithms, including EM algorithms.

Our nice FLaMingoS are mainly:

* mixRHLP;
* mixHMM;
* mixHMMR.

The models and algorithms are developped and written in Matlab by Faicel 
Chamroukhi, and translated and designed into R packages by Florian Lecocq, 
Marius Bartcus and Faicel Chamroukhi.

# Installation

You can install the **flamingos** package from [GitHub](https://github.com/fchamroukhi/FLaMingoS) with:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("fchamroukhi/FLaMingoS")
```

To build *vignettes* for examples of usage, type the command below instead:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("fchamroukhi/FLaMingoS", 
                         build_opts = c("--no-resave-data", "--no-manual"), 
                         build_vignettes = TRUE)
```

Use the following command to display vignettes:

```{r, eval = FALSE}
browseVignettes("FLaMingoS")
```

# Usage

```{r, message = FALSE}
library(flamingos)
```

<details>
  <summary>mixRHLP</summary>

```{r, message = FALSE}
data("toydataset")

G <- 3 # Number of clusters
K <- 3 # Number of regimes (polynomial regression components)
p <- 1 # Degree of the polynomials
q <- 1 # Order of the logistic regression (by default 1 for contiguous segmentation)
variance_type <- "heteroskedastic" # "heteroskedastic" or "homoskedastic" model

n_tries <- 1
max_iter <- 1000
threshold <- 1e-5
verbose <- TRUE
verbose_IRLS <- FALSE
init_kmeans <- TRUE

mixrhlp <- emMixRHLP(toydataset$x, t(as.matrix(toydataset[,2:ncol(toydataset)])), 
                     G, K, p, q, variance_type, init_kmeans, n_tries, max_iter, 
                     threshold, verbose, verbose_IRLS)

mixrhlp$summary()

mixrhlp$plot()
```

</details>

<details>
  <summary>mixHMM</summary>

```{r, message = FALSE}
data("toydataset")

K <- 3 # Number of clusters
R <- 3 # Number of regimes (HMM states)
variance_type <- "heteroskedastic" # "heteroskedastic" or "homoskedastic" model

ordered_states <- TRUE
n_tries <- 1
max_iter <- 1000
init_kmeans <- TRUE
threshold <- 1e-6
verbose <- TRUE

mixhmm <- emMixHMM(t(toydataset[,2:ncol(toydataset)]), K, R, variance_type, ordered_states, init_kmeans, n_tries, max_iter, threshold, verbose)

mixhmm$summary()

mixhmm$plot()
```

</details>

<details>
  <summary>mixHMMR</summary>
  
```{r, message = FALSE}
data("toydataset")

K <- 3 # Number of clusters
R <- 3 # Number of regimes/states
p <- 1 # Degree of the polynomial regression
variance_type <- "heteroskedastic" # "heteroskedastic" or "homoskedastic" model

ordered_states <- TRUE
n_tries <- 1
max_iter <- 1000
init_kmeans <- TRUE
threshold <- 1e-6
verbose <- TRUE

mixhmmr <- emMixHMMR(toydataset$x, t(toydataset[,2:ncol(toydataset)]), K, R, p,
                     variance_type, ordered_states, init_kmeans, n_tries, max_iter,
                     threshold, verbose)

mixhmmr$summary()

mixhmmr$plot()
```

</details>

# References
